\section{Unit Commitment Problem}
\label{fundamentals:ucp}

The Unit Commitment Problem (UCP) generally is concerned with the scheduling or ``commitment'' of thermal power plants over a given period.
Thermal power plants can be coal, oil, gas, or nuclear power plants.
The power plants should be scheduled such that the power demand or ``network load'' at each moment of the period is satisfied by the power output of the power plants.
While satisfying the demand, the sum of the fuel costs ($f_{i, t}$) should be minimal.
The fuel cost depends on the commitment of each power plant at each time ($u_{i, t}$), the power output of each power plant at each time ($p_{i, t}$), the power plant-specific cost function coefficients ($A_i$, $B_i$ and $C_i$), as well as start-up and shut-down costs ($A_{i}^{U}$ and $A_{i}^{D}$).
Other than the demand, the problem also considers various other constraints of the power plants.
These include the minimum and maximum power output of each plant ($P_{min, i}$ and $P_{max, i}$), the ramping constraints of each plant, and the minimum up and down-time~\cite{Baldick1995}.

This work only considers a subset of all possible constraints.
The demand, the minimum and maximum power output of the individual plant, and the startup and shutdown costs are considered.
So the goal is to minimize the sum of the cost functions ($f_{i, t}$) that also considers the startup and shutdown-costs.
Also, at each time instance, the combined power output satisfies the demand, and each power output does not violate the minimum and maximum power output of the power plant.

The UCP, this work considers, is non-linear because of the quadratic cost functions ($f_{i, t}$).
It also has floating-point variables and binary variables, where binary variables are represented as integer variables with domain $\{0, 1\}$.
The class of mixed-integer non-linear problems (MINLP) is a class of optimization problems, with a non-linear objective function, integer and floating-point variables, and various constraints on the variables.
For that reason, the UCPs often are formulated as MINLPs.
These models are non-convex in the case of the UCP due to the binary nature of the commitment variables ($u_{i, t}$)~\cite{Baldick1995, Abujarad2017}.
