\section{Implementation for Gate-based Quantum Computers}
\label{implement:gate.qubo}

The implementation for the gate-based quantum computers uses the Qiskit framework.
Qiskit is an open-source framework for quantum computing on gate-based quantum computers.
IBM Research founded Qiskit~\cite{QiskitWeb, QiskitGitHub}.
After the program instantiates the QUBO using the \texttt{QuadraticProgram} class of the framework, it uses the class \texttt{GroverOptimizer} to optimize the QUBO.
This class handles executing the Grover Optimization algorithm that section \ref{fundamentals:quantum.grover.optimization} describes.
That includes building the quantum circuits of Grover algorithm instances for every iteration and the classical computation in between iterations.

\subsubsection{Variables}

In this implementation, the variables are not implicit as with the UQO-client in section \ref{implementation:annealing.qubo.variables}.
The program instantiates all binary variables of the QUBO at the beginning of building the QUBO instance.
It assigns a name to every variable.
That name holds the indices of the corresponding power plant $i$, time $t$, and power output level $k$.

\subsubsection{Quadratic Biases}

The program adds the same quadratic biases as the implementation for annealing-based hardware that is described in section \ref{implementation:annealing.qubo.quadratic}.
It stores the biases in a Python \texttt{dict} with keys that are pairs of strings.
The strings are the names of the variables.

\subsubsection{Linear Biases}

The program adds the same linear biases as the implementation for annealing-based hardware that is described in section \ref{implementation:annealing.qubo.linear}.
It stores the biases in a Python \texttt{dict} with keys that are strings.
The strings are the names of the variables.

\subsubsection{Canstant Bias}

As mentioned before in section \ref{implementation:annealing.qubo.constant}, the constant bias does not change the input that produces an optimum of the QUBO.
But with this framework, the interface allows for a constant bias to be added to the QUBO.
The implementation computes the bias once, as specified in the formula (\ref{formula:qubo.result.constant}, and adds it to the QUBO instance.
