\section{Quantum Computing}

Quantum computers use quantum bits (qubits) instead of normal bits that classical computers use.
While a bit can be either in the state $0$ or $1$, a qubit can be in a so-called superposition of two states.
States of qubits are generally written using the Dirac-Notation, also known as the Bra-Ket-Notation
The two states, the superposition is a combination of, are called the basis.
The most basic basis is the basis $\{ \ket{0}, \ket{1} \}$.
The formula (\ref{formula:quantum.superposition}) describes such a superposition.
When one measures the state of the qubit, it collapses into one of the base states, which is the result of the measurement.
The probability of either basis state being measured is the square of the the complex amplitude of the basis state in the superposition.
\cite{Vedral1998}
\begin{subequations}
\begin{align}
  \label{formula:quantum.superposition}
  \ket{\phi} & = \alpha \cdot \ket{0} + \beta \cdot \ket{1}
  = \begin{pmatrix}
    \alpha \\ \beta
  \end{pmatrix}
  & \text{with } \alpha, \beta \in \mathbb{C}, \alpha^2 + \beta^2 = 1
  \\
  p_0 & = \alpha^2
\end{align}
\end{subequations}

Multiple qubits chained together form a quantum register.
In such a register, the measurement results of one qubit might depend on the measurement results of other qubits.
This is called entanglement.
The formula (\ref{formula:quantum.superposition.register}) describes a quantum register with $n$ qubits.
If one can't separate the formula into single qubits, the state is entangled.
The probability of measuring a specific state of the quantum register is given by the amplitude of that state squared.
\cite{Vedral1998}
\begin{subequations}
\begin{align}
  \label{formula:quantum.superposition.register}
  \ket{\Phi} & = \sum_{x \in \{0, 1\}^n} \alpha_x \cdot \ket{x}
  = \begin{pmatrix}
    \alpha_{0 \ldots 00} \\ \alpha_{0 \ldots 01} \\ \alpha_{0 \ldots 10} \\ \ldots \\ \alpha_{1 \ldots 11}
  \end{pmatrix}
  & \text{with } \forall x \in \{0, 1\}^n: \alpha_x \in \mathbb{C},
  \sum_{x \in \{0, 1\}^n} \alpha_x^2 = 1
  \\
  p_x & = \alpha_x^2
\end{align}
\end{subequations}

\input{02_Background/03_Quantum/01_annealing}
\input{02_Background/03_Quantum/02_gatebased}
