\section{Unit Commitment Problem} \label{intro:ucp}

The Unit Commitment Problem (UCP) generally is concerned with the scheduling or ''commitment''
of thermal power plants over a given time period.
Where thermal power plants can be coal, oil, gas or nuclear power plants.
The commitment of the power plants should be scheduled in such a way,
that the power demand or ''netwrok load'' at each moment of the time period
is satisfied by the power output of the power plants.
While satisfying the netwrok load, the fuel cost should be minimal.
The fuel cost depends on the commitment of each power plant at each time ($u_{i, t}$),
the power output of each power plant at each time ($p_{i, t}$),
the power plant specific cost function coefficients ($A_i$, $B_i$ and $C_i$),
as well as start-up and shut-down costs ($A_{i}^{U}$ and $A_{i}^{D}$).
Other than the netwrok load, the problem also consideres various other constraints of the power plants.
These include the minimum and maximum power output of each plant ($P_{min,i}$ and $P_{max,i}$),
the ramping constraints of each plant,
and the minimum up- and down-time.
\cite{Baldick1995}

In this paper, only the network load serves as a constraint to the commitment of the thermal power plants.
So it consists of the cost function $f_{i, t}$ that is to be minimized,
the network load constraint for each time $t$,
and the power output constraint for each unit $i$ and time $t$.

The UCP is non-linear in nature, because of the quadratic cost function $f_{i, t}$.
It also has floating-point variables as well as binary variables,
where binary variables can be represented as integer variables with domain $\{0, 1\}$.
The class of mixed-integer nonlinear problems (MINLP) is a class of optimization problems,
with a non-linear objective funtion,
integer and floating-point variables,
as well as various constraints on the variables.
This is the reason, that the UCPs are often formulated as MINLPs.
These models are non-convex in the case of the UCP, due to the binary nature of the commitment variables $u_{i, t}$.
\cite{Baldick1995, Abujarad2017}
